Effective Reionization Likelihood from Planck 2018 Data (?)

### 2020-12-05 paper/rei.tex

\begin{figure*}
%\includegraphics[width=0.7\textwidth]{plots/plot_mj_triangle_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite_srollv2_1015_wTauTrajectory_pl15_wTanhML.png}
\includegraphics[width=1.0\textwidth]{paper/plots/plot_mj_triangle_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite_srollv2_1015_wTauTrajectory_pl15_wTanhML_wGaussEllipse.pdf}

@@

\begin{figure}
\includegraphics[width=0.40\textwidth]{plots/pl18_pc_zmax30_pliklite_srollv2_1015_tau_posterior_fraccov_1p0_burnin_10000_yes_norm_gaussian0p1_0p12_0p14.pdf}
\caption{Posterior of total optical depth $\tau$: full likelihood (solid) vs effective likelihood (dotted) with f = 0.14 [remove more curves?]. The results agree well; the effective likelihood gives a slightly broader posterior because the kernel density estimate in the PC space introduces smoothing at roughly $\sim$7\% level in the parameter posterior corresponding to $f = 0.14$.
}
\label{fig:tanh_}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=0.450\textwidth]{plots/plot_tau_gtz.pdf}
\caption{Same as \reffig{plot_taugtz_PC_vs_tanh}, but superimposed with the cumulative optical depth $\tau(z, \zmax)$ of the best-fit two-step model. The two-step model is a toy model that adds a high-$z$ ionization plateau to the standard tanh model with one additional parameter. Compared to the cumulative $\tau$ distributions from PCs, the best-fit step-model model is within the 95\% upper limit of the cumulative $\tau$ constraints at all redshifts. 
}
\label{fig:plot_taugtz_two_step_best_fit}
\end{figure}

\begin{figure}
\includegraphics[width=0.40\textwidth]{plots/pl18_tanh_highz_kde_f0p14_tau_z_to_zstart_plot_tau_gtz_dz0p1.pdf}
\caption{
}
\label{fig:plot_taugtz_two_step_contours}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.5\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_plikfull_and_pl18_tanh_post_plikfull.pdf}
\caption{PC zmax = 30 vs tanh chains with plik\_full\_TTTEEE for the high-l likelihood.
}
\label{fig:plot_taugtz_PC_vs_tanh}
\end{figure}

>>>>

\begin{figure*}
%\includegraphics[width=0.7\textwidth]{plots/plot_mj_triangle_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite_srollv2_1015_wTauTrajectory_pl15_wTanhML.png}
\includegraphics[width=0.8\textwidth]{paper/plots/plot_mj_triangle_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite_srollv2_1015_wTauTrajectory_pl15_wTanhML_wGaussEllipse.pdf}

@@

\begin{figure}
\includegraphics[width=0.40\textwidth]{plots/pl18_pc_zmax30_pliklite_srollv2_1015_tau_posterior_fraccov_1p0_burnin_10000_yes_norm_gaussian0p1_0p12_0p14.pdf}
\caption{Posterior of total optical depth $\tau$: full likelihood (solid) vs effective likelihood (dotted) with f = 0.14 [remove more curves?]. The results agree well; the effective likelihood gives a slightly broader posterior because the kernel density estimate in the PC space introduces smoothing at roughly $\sim$7\% level in the parameter posterior corresponding to $f = 0.14$.
}
\label{fig:tanh}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.5\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_plikfull_and_pl18_tanh_post_plikfull.pdf}
\caption{Tanh chains with plik\_full\_TTTEEE for the high-l likelihood. [remove PC zmax curve; add PC filtered version]
}
\label{fig:plot_taugtz_PC_vs_tanh}
\end{figure}

@@

%PC w/ ML model from 2parameter model (tauhi>0.02)
%\begin{figure}[t]
%\includegraphics[width=0.450\textwidth]{plots/plot_tau_gtz.pdf}
%\caption{Same as \reffig{plot_taugtz_PC_vs_tanh}, but superimposed with the cumulative optical depth $\tau(z, \zmax)$ of the best-fit two-step model. The two-step model is a toy model that adds a high-$z$ ionization plateau to the standard tanh model with one additional parameter. Compared to the cumulative $\tau$ distributions from PCs, the best-fit two-step model is within the 95\% upper limit of the cumulative $\tau$ constraints at all redshifts. 
%}
%\label{fig:plot_taugtz_two_step_best_fit}
%\end{figure}

\begin{figure}
\includegraphics[width=0.40\textwidth]{plots/pl18_tanh_highz_kde_f0p14_tau_z_to_zstart_plot_tau_gtz_dz0p1.pdf}
\caption{The 68\% and 95\% C.L. constraints on the cumulative optical depth $\tau(z, \zmax)$ for the two-step model, which allows for high-redshift ionization up to $\zmax =30$. note that a physical model with $\tau(15, \zmax) = 0.02$ is still allowed at the 95\% C.L. whereas the Planck FlexKnot analysis would have ruled it out with their $\tau(15, \zmax) < 0.007$ 95\% upper limit. [add not PC filtered version]
}
\label{fig:plot_taugtz_two_step_contours}
\end{figure}

@@
